Tunable Spectral Ordering of Magnetic Plasmons

### 2017-05-23 may_paper/draft_2.0.tex
more paper stuff

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The "tocentry" environment can be used to create an entry for the
%% graphical table of contents. It is given here as some journals
%% require that it is printed as part of the abstract page. It will
%% be automatically moved as appropriate.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tocentry}
\includegraphics{toc_graphic.pdf}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The abstract environment will automatically gobble the contents
%% if an abstract is not used by the target journal.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Ring-like assemblies of metal nanoparticles that exhibit magnetic resonances, called magnetic plasmon oligomers, have been of recent interest as negative-index metamaterials and light-harvesting devices. For these reasons, it is imperative to understand the properties of such systems on the single- to few-oligomer scale. We show through theory and simulation that the energy ordering of the magnetic resonances of few-oligomer systems depends on size, scale, and environment in ways that purely electric plasmons do not. We show that the dynamic ordering of the eigenmodes of magnetic systems is due entirely to retardation effects and can be understood by inspecting the intermediate- and far-field contributions which are excluded in the quasistatic approximation. We highlight the versatility and tunability of magnetic plasmon oligomers, elucidating a previously unexplored physical phenomenon and suggesting future applications of magnetic plasmons in highly sensitive detection methods. 
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Start the main part of the manuscript here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Metal nanoparticles (MNPs) support collective resonances of their conduction electrons at optical frequencies. These localized surface plasmon resonances (LSPRs) can interact with each other in assemblies to produce hybridized resonances, much like the hybridization of atomic orbitals in molecules\cite{Lucas1976,ARAVIND1981,Xu1995,Mischenko1995}. When these MNPs are arranged in rings, the single LSPRs can give rise to a collective mode that produces an oscillating magnetic dipole in the center of the ring\cite{Alu2006,Alu2008,Liu2011,Nord2006,Cherqui2014,Cherqui2016}. Such systems are known as magnetic plasmon oligomers and have been of intense focus due to their potential applications in sensing\cite{Zia2010trans,Noginova2008trans,Wang:13,Fan2015,Wei2015,Shvets2012,Altug2012bio,Nord2011fano}, lensing\cite{Fang2005,Valentine2008}, cloaking\cite{Shalaev2008}, and information processing\cite{Zhang2006,NordHal2011,NordHal2012}. In Cherqui's 2014 work on magnetic plasmons, a quasistatic, electric dipole tight-binding model was used to describe the magnetic systems\cite{Cherqui2014}; we adapt this model to expand on the results of that work. Cherqui's model considered only the electric near-field of the single-particle plasmons and only incorporated nearest-neighbor interactions. As a result, while it accurately predicted the magnetic eigenmodes, it inaccurately described their energy ordering as confirmed by simulation. An explanation was needed to determine why the tight-binding model would predict different energy-ordering than full-wave simulations.

@@

where $\textbf{P}_i$ are the momenta conjugate to the plasmon coordinates $\textbf{X}_{i}$, $\omega_{\textrm{sp},i}$ are the individual LSPR frequencies of each oscillator, $m_{\textrm{sp},i}$ are the LSPR effective masses and $\boldsymbol{\Lambda}_{ij}$ is the fully retarded dipole-dipole relay tensor (expanded below)\cite{jackson_classical_1999}. To make this Hamiltonian more manageable, it is nondimensionalized using $\textbf{Q}_i = \left(m_{\textrm{sp}}\omega_{\textrm{sp}}/\hbar\right)^{\frac{1}{2}}\textbf{X}_i$ and $\boldsymbol{\Pi}_i = \textbf{P}_i/\sqrt{\hbar m_{\textrm{sp}}\omega_{\textrm{sp}}}$. Substituting into Equation~\ref{elec_hammy_1} and expanding $\boldsymbol{\Lambda}_{ij}$, we get:

\begin{equation}
\begin{aligned}
H = 
\frac{\hbar\omega_{sp}}{2}\sum_{i}^{n}[\boldsymbol{\Pi}_i^2 + \textbf{Q}_i^2] - \frac{\hbar\omega_{sp}}{2\varepsilon_b}\sum_{i>j}\{g_{ij}^{\textrm{NF}}\left[3(\textbf{Q}_i\cdot\hat{\textbf{n}}_{ij})(\hat{\textbf{n}}_{ij}\cdot\textbf{Q}_j) - \textbf{Q}_i\cdot\textbf{Q}_j\right] \\
+ g_{ij}^{\textrm{IF}}\left[3(\textbf{Q}_i\cdot\hat{\textbf{n}}_{ij})(\hat{\textbf{n}}_{ij}\cdot\textbf{Q}_j) -\textbf{Q}_i\cdot\textbf{Q}_j\right] \\ 
- g_{ij}^{\textrm{FF}}\left[(\textbf{Q}_i\cdot\hat{\textbf{n}}_{ij})(\hat{\textbf{n}}_{ij}\cdot\textbf{Q}_j) -\textbf{Q}_i\cdot\textbf{Q}_j\right]\},\label{elec_hammy_2}
\end{aligned}
\end{equation}

In this Hamiltonian we introduce the near, intermediate, and far-field coupling terms: $g_{ij}^{\textrm{NF}} = \frac{\alpha_{sp}'}{r_{ij}^3}\cos\left(k r_{ij}\right)$, $g_{ij}^{\textrm{IF}} = \frac{\alpha_{sp}'k}{r_{ij}^2}\sin\left(k r_{ij}\right)$, and $g_{ij}^{\textrm{FF}} = \frac{\alpha_{sp}'k^2}{r_{ij}}\cos\left(k r_{ij}\right)$, respectively, with wavenumber $k = \sqrt{\varepsilon_b}\frac{\omega}{c}$. Additionally, $r_{ij}$ is the distance between the ith and jth LSPRs and $\hat{\textbf{n}}_{ij}$ is the unit vector connecting two LSPRs. We further incorporate retardation effects by considering the lattice dispersion in the polarizability $\alpha_{sp}' = \left(\alpha_{sp}^{-1} - i\frac{2}{3}k^3\right)^{-1}$ with $\alpha_{sp} = r_0^3\frac{3}{\varepsilon_{\infty}-2\varepsilon_b}$. Including these terms, we have incorporated all retardation effects associated with point dipoles\cite{Purcell1973,Draine1993}.

@@

In this work, we model silver nanoparticles using a Drude model with $\omega_p = 9.1$ eV, $\varepsilon_{\infty} = 3.77$, and $\gamma = 0.003$ eV. Note that we have greatly reduced the damping constant in order to better resolve the magnetic modes in the simulations. The oligomer unit cell is a six-member ring, with silver nanoparticles located at the vertices of a regular hexagon. We explore and manipulate three magnetic oligomer systems: a twomer, a linear threemer, and a triangular threemer. The number of rings in a magnetic system corresponds to the number of magnetic modes in the system\cite{Cherqui2014}. The twomer supports an in-phase mode (North-North, or NN) and an out-of-phase mode (North-South, or NS). The linear threemer supports an all in-phase mode (All-North, or AN), a minimally out-of-phase mode (North-South, or NS), and a maximally out-of-phase mode (North-South-North, or NSN). The triangular threemer supports an all in-phase mode (All-North, or AN) and two degenerate out-of-phase modes (North-South, or NS). These modes and their relative magnetic fields are depicted in Figures~\ref{magmodes},~\ref{dielectric}, and ~\ref{spacing}. In each exploration, the particles have radius $r_0$ and nearest-neighbor spacing $r_{\textrm{nn}}$. In the first set of model calculations, we compare to full-wave simulations to verify that the model accurately captures the properties of the systems, but beyond that we cease comparison to simulation in order to focus on the predictive power of the model. The first calculations, depicted in Figure~\ref{magmodes} show how the magnetic modes of the twomer and threemers are impacted by the overall scale of the system. In these calculations, the nearest neighbor distances are held at $r_{\textrm{nn}} = 3 \times r_0$ while $r_0$ varies from 1 nm to 30 nm.

@@

where $\textbf{p}_{i}$ is an eigenvector and $\boldsymbol{\Lambda}_{ij}$ is the dipole relay tensor connecting all of the electric dipoles. This calculation serves as a further confirmation of the mode-switching, as the interaction strengths follow the eigenvalues.

\begin{figure}
\centering
\includegraphics[height=0.6\paperheight]{interaction_strength.pdf}
\caption{Interactions strengths for the magnetic modes of the twomer (first row), linear threemer (second row), and triangular threemer (third row). We plot as a function of scaling the total interaction strength between the electric plasmons (solid line), the near-field and intermediate-field interaction strength summed (circles), and the far-field interaction strength (squares). In all three systems, the total interaction strengths are the same as those in Figure~\ref{magmodes} and so exhibit two mode crossings. The near- and intermediate- fields do not exhibit any crossings at all, and the interaction strengths for each mode simply diverge more and more with greater scaling. The far-field terms do exhibit one crossing towards the larger end of the scaling spectrum, and it is this interplay of far-field with near- and intermediate-field interactions that causes the mode-switching in these magnetic systems.}
\label{interactions}
\end{figure}

To gain a more complete understanding of why mode-switching does occur in magnetic systems, we compute not only the total interaction strength for the electric plasmons of each magnetic mode, but we break that calculation into its near-, intermediate-, and far-field components. The results of this calculation are displayed in Figure~\ref{interactions}. This exploration shows definitively that the near- and intermediate-field terms contribute a total shift of the interaction strength, but the far-field term alone contributes to the mode switching. This can be seen quite clearly in the dipole relay tensors for the near- and intermediate-field,

\begin{equation}
\begin{aligned}
\boldsymbol{\Lambda}_{ij}^{\textrm{NF,IF}} = 3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} -\textbf{1}
\label{lambda_NFIF}
\end{aligned}
\end{equation}

and the far-field,

\begin{equation}
\begin{aligned}
\boldsymbol{\Lambda}_{ij}^{\textrm{FF}} = \textbf{1}-\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij}
\label{lambda_FF}
\end{aligned}
\end{equation}

where \textbf{1} is the unit dyad. Looking at Equations~\ref{lambda_NFIF} and ~\ref{lambda_FF}, we see that the ordering of the terms is switched. The form of Equation~\ref{lambda_NFIF} shows that linearly oriented dipoles contribute more to the interaction energy than parallel dipoles. However, Equation~\ref{lambda_FF} has no contribution from pairs of linearly oriented dipoles and only has equal and opposite contributions from pairs of parallel dipoles [\textbf{should I cite the JPCC Steve wrote? Lots about ordering and arrangements of dipoles...}]. Furthermore, the difference in sign on the two dyadic terms in the dipole relay tensors implies that the contributions to the interaction energy from those terms will be of opposite sign for the same pairs of dipoles. The distance-dependence of each field term for different pairs of dipoles is further outlined in Figure~\ref{dimers}. The opposition of signs, as well as the crossing in the far-field interaction term, are enough to explain the phenomenon of mode-switching in magnetic oligomers.

\begin{figure}
\centering
\includegraphics[width=0.6\paperwidth]{dimer_interaction.pdf}
\caption{Relative interaction strengths for the four possible dipole arrangements of a nanoparticle dimer: collinear (a), parallel (b), anti-collinear (c), and anti-parallel (d). Plotted are the near-field (blue), intermediate-field (orange), far-field (green), and total (black, dashed) interaction strengths for each set of dipoles as a function of dipole-dipole distance. Interestingly, and stemming from the form of the dipole relay tensor, the far-field interaction term is zero for both pairs of linear dipoles. From these plots, it can be seen that the favorability of a specific dipole arrangement depends on the separation between the dipoles. This can be seen in the fact that each part of the field depends differently on the separation, and each field term contains an oscillating term. At short length scales, the interaction is dominated by the near-field. However, as the distance increases, the interaction is dominated by the intermediate field (a and c) or the far-field (b and d). As a result, there are separation distances at which normally unfavorable arrangements become favorable. Since magnetic oligomers can be described through pairwise interactions of electric dipoles, it follows that the eigenvalues must also change order as different arrangements of electric dipoles become more and less favorable.}
\label{dimers}
\end{figure}

We have convinced ourselves that 1) the quasistatic, nearest-neighbors tight-binding model does not contain enough information to agree with fully retarded electrodynamics simulations, 2) those same simulations conform to the results from an updated tight-binding model that incorporates retardation effects and all-particle interactions and 3) the unexpected mode switching exhibited by these magnetic systems is entirely physical and explicable by the varying, distance-dependent decay and oscillation of the electric field terms. With a working model and a basic physical understanding of these three systems, we now perform a series of computations to look at its tunable properties. In the previous section, the scale of the systems was changed. However, this would be impossible to manipulate in a laboratory. We focus on properties with experimental analogues, namely, the dielectric constant of the embedding medium and the nearest-neighbor spacing between nanoparticles.

@@

In order to justify the next set of model calculations, we refer to research on flowing liquid crystal over MNP aggregates and, in real-time, adjusting the refractive index of the MNP environment, influencing the resonance frequencies of the system\cite{odom_lasing}. We apply this concept to our tight-binding model to determine if this has any implications on the properties of magnetic oligomers. What we find is that, as expected, increasing the real-valued dielectric constant of the background decreases the resonance frequency of the collective modes. Furthermore, the embedding medium influences the energy-ordering of the eigenvalues. Results of one of our explorations are summarized in Figure~\ref{dielectric}. As the dielectric constant of the medium increases, the eigenmodes collapse onto each other, and eventually converge with the single-particle frequency. Because the modes collapse so quickly and appear to overlap at all values of $\varepsilon_b$, Figure~\ref{dielectric}b displays the difference in energy between all of the eigenmodes of each system. The values of $\varepsilon_b$ where the differences cross zero signify mode-crossing. 
From these two observations we conclude that increasing the dielectric constant of the embedding medium weakens the overall inter-particle interactions. However, this occurs differently for each of the parts of the interaction. All of the field terms contain similar $k$-dependence through $\alpha_{\textrm{sp}}'$ and the trigonometric terms, but focusing on how each term depends differently on $k$ in the numerator of the coupling constants (Equation~\ref{elec_hammy_2}) reveals how the dielectric constant influences the electric field. The near-field term contains no other $k$-dependence, and so is reduced by one factor of $\varepsilon_b$. The intermediate-field term is linear in $k$, so it is reduced by a factor of $\sqrt{\varepsilon_b}$. Lastly, the far-field term is quadratic in $k$, so all $\varepsilon_b$-dependence is removed, besides that dependence previously mentioned. At higher values of the dielectric constant the far-field term dominates, much like the way particles that are far apart interact primarily through their far-fields (Figure~\ref{dimers}b and d). In other words, embedding magnetic systems in some dielectric medium causes them to act as though they are larger, effectively increasing their scale. This insight provides an experimental route to directly choosing the energy-ordering of magnetic modes, but the reduced splitting between modes might make such an experiment infeasible.

\begin{figure}
\centering
\includegraphics[width=.6\paperwidth]{spacing_study.pdf}
\caption{Magnetic mode eigenvalues for the twomer (first row), linear threemer (second row), and triangular threemer (third row) with particle sizes of 15 nm (column a) and 30 nm (column b) as a function of nearest neighbor particle separation in units of radii. As the separation distance increases, the magnetic mode eigenvalues converge to and oscillate about the single particle frequency, exhibiting multiple crossings. As in Equation~\ref{elec_hammy_2}, the interaction strength decays with increasing separation and oscillates due to its dependence on trigonometric functions.}
\label{spacing}
\end{figure}

There is also active research on tuning the size and shape of a plasmonic aggregate using various polymers\cite{Ginger2017} or DNA\cite{DanLuo2009,NaLiu2017}. Here, we implement the idea of continuously distorting the nearest-neighbor spacing, from touching to tens of radii apart. We present data for particle radii of 15 nm and 30 nm in Figure~\ref{spacing}a and b, respectively. The results of these model calculations are reminiscent of the results in Figure~\ref{dimers} in that the eigenmodes oscillate about each other as the particles move farther apart. In addition, similarly to Figure~\ref{dielectric}, at very large distances the eigenvalues converge to the single LSPR frequency, exhibiting small amplitude oscillations. This is indicative of the coupling falling very near to zero. It is clear that this method, as opposed to the method of tuning the dielectric constant of the background, offers a much greater degree of tunability. Designing a system in which the inter-particle spacing could be varied in discrete steps would lead to the ability to directly choose the resonance frequency of a specific magnetic mode. Furthermore, being able to directly detect the frequency of the magnetic mode optically could turn such magnetic systems into thermometers, pH probes, or detectors of any environmental factor that would change the size of the embedding polymer.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The "tocentry" environment can be used to create an entry for the
%% graphical table of contents. It is given here as some journals
%% require that it is printed as part of the abstract page. It will
%% be automatically moved as appropriate.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tocentry}
\includegraphics{toc_graphic_2.pdf}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The abstract environment will automatically gobble the contents
%% if an abstract is not used by the target journal.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Ring-like assemblies of metal nanoparticles that exhibit magnetic resonances, called magnetic plasmon oligomers, have been of recent interest as negative-index metamaterials and light-harvesting devices. For these reasons, it is imperative to understand the properties of such systems on the single- to few-oligomer scale. We show through theory and simulation that the energy ordering of the magnetic resonances of few-oligomer systems depends on size, scale, and environment in ways that purely electric plasmons do not. The dynamic ordering of the eigenmodes of magnetic systems is due entirely to retardation effects and can be understood by inspecting the intermediate- and far-field contributions which are excluded in the quasistatic approximation. This work highlights the versatility and tunability of magnetic plasmon oligomers, elucidating a previously unexplored physical phenomenon and suggesting future applications of magnetic plasmons in highly sensitive detection methods. 
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Start the main part of the manuscript here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Metal nanoparticles (MNPs) support collective resonances of their conduction electrons at optical frequencies. These localized surface plasmon resonances (LSPRs) can interact with each other in assemblies to produce hybridized resonances, much like the hybridization of atomic orbitals in molecules\cite{Lucas1976,ARAVIND1981,Xu1995,Mischenko1995}. When these MNPs are arranged in rings, the single LSPRs can give rise to a collective mode that produces an oscillating magnetic dipole in the center of the ring\cite{Alu2006,Alu2008,Liu2011,Nord2006,Cherqui2014,Cherqui2016}. Such systems are known as magnetic plasmon oligomers and have been of intense focus due to their potential applications in sensing\cite{Zia2010trans,Noginova2008trans,Wang:13,Fan2015,Wei2015,Shvets2012,Altug2012bio,Nord2011fano}, lensing\cite{Fang2005,Valentine2008}, cloaking\cite{Shalaev2008}, and information processing\cite{Zhang2006,NordHal2011,NordHal2012}. In Cherqui's 2014 work on magnetic plasmons, a quasistatic, electric dipole tight-binding model was used to describe the magnetic systems\cite{Cherqui2014}; we adapt this model to expand on the results of that work. Cherqui's model considered only the electric near-field of the single-particle plasmons and only incorporated nearest-neighbor interactions. As a result, while it accurately predicted the magnetic eigenmodes, it inaccurately described the energy ordering predicted by full-wave simulation. An explanation was needed to determine why the tight-binding model would predict different energy-ordering.

@@

\noindent where $\textbf{P}_i$ are the momenta conjugate to the plasmon coordinates $\textbf{X}_{i}$, $\omega_{\textrm{sp},i}$ are the individual LSPR frequencies of each oscillator, $m_{\textrm{sp},i}$ are the LSPR effective masses and $\boldsymbol{\Lambda}_{ij}$ is the fully retarded dipole-dipole relay tensor (expanded below)\cite{jackson_classical_1999}. To make this Hamiltonian more manageable, it is nondimensionalized using $\textbf{Q}_i = \left(m_{\textrm{sp}}\omega_{\textrm{sp}}/\hbar\right)^{\frac{1}{2}}\textbf{X}_i$ and $\boldsymbol{\Pi}_i = \textbf{P}_i/\sqrt{\hbar m_{\textrm{sp}}\omega_{\textrm{sp}}}$. Substituting into Equation~\ref{elec_hammy_1} and expanding $\boldsymbol{\Lambda}_{ij}$, we get:

\begin{equation}
\begin{aligned}
H = 
\frac{\hbar\omega_{sp}}{2}\sum_{i}^{n}[\boldsymbol{\Pi}_i^2 + \textbf{Q}_i^2] - \frac{\hbar\omega_{sp}}{\varepsilon_b}\sum_{i>j}\{g_{ij}^{\textrm{NF}}\left[3(\textbf{Q}_i\cdot\hat{\textbf{n}}_{ij})(\hat{\textbf{n}}_{ij}\cdot\textbf{Q}_j) - \textbf{Q}_i\cdot\textbf{Q}_j\right] \\
+ g_{ij}^{\textrm{IF}}\left[3(\textbf{Q}_i\cdot\hat{\textbf{n}}_{ij})(\hat{\textbf{n}}_{ij}\cdot\textbf{Q}_j) -\textbf{Q}_i\cdot\textbf{Q}_j\right] \\ 
- g_{ij}^{\textrm{FF}}\left[(\textbf{Q}_i\cdot\hat{\textbf{n}}_{ij})(\hat{\textbf{n}}_{ij}\cdot\textbf{Q}_j) -\textbf{Q}_i\cdot\textbf{Q}_j\right]\},\label{elec_hammy_2}
\end{aligned}
\end{equation}

In this Hamiltonian we introduce the near, intermediate, and far-field coupling terms: $g_{ij}^{\textrm{NF}} = \frac{\alpha_{sp}'}{r_{ij}^3}\cos\left(k r_{ij}\right)$, $g_{ij}^{\textrm{IF}} = \frac{\alpha_{sp}'k}{r_{ij}^2}\sin\left(k r_{ij}\right)$, and $g_{ij}^{\textrm{FF}} = \frac{\alpha_{sp}'k^2}{r_{ij}}\cos\left(k r_{ij}\right)$, respectively, with wavenumber $k = \sqrt{\varepsilon_b}\frac{\omega}{c}$ and $\omega$ is the frequency of each collective mode. Additionally, $r_{ij}$ is the distance between the ith and jth LSPRs and $\hat{\textbf{n}}_{ij}$ is the unit vector connecting two LSPRs. We further incorporate retardation effects by considering the lattice dispersion in the polarizability $\alpha_{sp}' = \left(\alpha_{sp}^{-1} - i\frac{2}{3}k^3\right)^{-1}$ with $\alpha_{sp} = r_0^3\frac{3}{\varepsilon_{\infty}-2\varepsilon_b}$. Including these terms, we have incorporated all retardation effects associated with point dipoles\cite{Purcell1973,Draine1993}.

@@

In this work, we model silver nanoparticles using a Drude model with $\omega_p = 9.1$ eV, $\varepsilon_{\infty} = 3.77$, and $\gamma = 0.003$ eV. Note that we have greatly reduced the damping constant in order to better resolve the magnetic modes in the simulations. The oligomer unit cell is a six-member ring, with silver nanoparticles located at the vertices of a regular hexagon. We explore and manipulate three magnetic oligomer systems: a twomer, a linear threemer, and a triangular threemer. The number of rings in a magnetic system corresponds to the number of magnetic modes in the system\cite{Cherqui2014}. The twomer supports an in-phase mode (North-North, or NN) and an out-of-phase mode (North-South, or NS). The linear threemer supports an all in-phase mode (All-North, or AN), a minimally out-of-phase mode (North-South, or NS), and a maximally out-of-phase mode (North-South-North, or NSN). The triangular threemer supports an all in-phase mode (All-North, or AN) and two degenerate out-of-phase modes (North-South, or NS). These modes and their relative magnetic fields are depicted as insets in Figures~\ref{magmodes},~\ref{interaction_strength},~\ref{dielectric}, and~\ref{spacing}. In each exploration, the particles have radius $r_0$ and nearest-neighbor spacing $r_{\textrm{nn}}$. In the first set of model calculations, we compare to full-wave simulations to verify that the model accurately captures the properties of the systems, but beyond that we cease comparison to simulation in order to focus on the predictive power of the model. The first calculations, depicted in Figure~\ref{magmodes} show how the magnetic modes of the twomer and threemers are impacted by the overall scale of the system. In these calculations, the nearest neighbor distances are held at $r_{\textrm{nn}} = 3 \times r_0$ while $r_0$ varies from 1 nm to 30 nm.

@@

\noindent where $\textbf{p}_{i}$ is an eigenvector and $\boldsymbol{\Lambda}_{ij}$ is the dipole relay tensor connecting all of the electric dipoles. This calculation serves as a further confirmation of the mode-switching, as the interaction strengths follow the eigenvalues.

\begin{figure}
\centering
\includegraphics{interaction_strength.pdf}
\caption{Interactions strengths for the magnetic modes of the twomer (first row), linear threemer (second row), and triangular threemer (third row). We plot the total interaction strength between the electric plasmons (solid line), the near-field and intermediate-field interaction strength summed (circles), and the far-field interaction strength (squares) as a function of scaling. The near- and intermediate- fields do not exhibit any crossings and diverge with greater scaling. The far-field terms exhibit one crossing. The interplay of far-field with near- and intermediate-field interactions causes mode-switching in magnetic systems.}
\label{interactions}
\end{figure}

To gain a more complete understanding of this mode-switchings, we compute the total interaction strength for the electric plasmons of each magnetic mode and we break that calculation into its near-, intermediate-, and far-field components. Figure~\ref{interactions} shows that the near- and intermediate-field terms contribute a total shift of the interaction strength, the far-field term alone contributes to the mode switching. This can be seen in the dipole relay tensors for the near- and intermediate-field,

\begin{equation}
\begin{aligned}
\boldsymbol{\Lambda}_{ij}^{\textrm{NF,IF}} \propto 3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} -\textbf{1}
\label{lambda_NFIF}
\end{aligned}
\end{equation}

\noindent and the far-field,

\begin{equation}
\begin{aligned}
\boldsymbol{\Lambda}_{ij}^{\textrm{FF}} \propto \textbf{1}-\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij}
\label{lambda_FF}
\end{aligned}
\end{equation}

\noindent where \textbf{1} is the unit dyad. Equations~\ref{lambda_NFIF} and ~\ref{lambda_FF} differ by a factor of 3 on the unit vector term and an overall factor of -1. For this reason, collinear and anticollinear interact more strongly in the near- and intermediate-fields. However, linearly oriented dipoles do not interact through the far-field at all and only parallel and antiparallel dipoles contribute to this term. [\textbf{should I cite the JPCC Steve wrote? Lots about ordering and arrangements of dipoles...}] The factor of -1 difference between Equations~\ref{lambda_NFIF} and ~\ref{lambda_FF} further implies that parallel and anti-parallel arrangements of dipoles will contribute interaction energies of opposite sign. The distance-dependence of each field term for different orientations of dipoles is further outlined in Figure~\ref{dimers}. The opposition of signs, as well as the crossing in the far-field interaction term, explain the phenomenon of mode-switching in magnetic oligomers.

\begin{figure}
\centering
\includegraphics{dimer_interaction.pdf}
\caption{Relative interaction strengths for the four possible dipole arrangements of a nanoparticle dimer: collinear (a), parallel (b), anti-collinear (c), and anti-parallel (d). Plotted are the near-field (blue), intermediate-field (orange), far-field (green), and total (black, dashed) interaction strengths for each set of dipoles as a function of dipole-dipole distance. Interestingly, and stemming from the form of the dipole relay tensor, the far-field interaction term is zero for both pairs of linear dipoles. From these plots, it can be seen that the favorability of a specific dipole arrangement depends on the separation between the dipoles. This can be seen in the fact that each part of the field depends differently on the separation, and each field term contains an oscillating term. At short length scales, the interaction is dominated by the near-field. However, as the distance increases, the interaction is dominated by the intermediate field (a and c) or the far-field (b and d). As a result, there are separation distances at which normally unfavorable arrangements become favorable. Since magnetic oligomers can be described through pairwise interactions of electric dipoles, it follows that the eigenvalues must also change order as different arrangements of electric dipoles become more and less favorable.}
\label{dimers}
\end{figure}

We have convinced ourselves that 1) the quasistatic, nearest-neighbors tight-binding model does not contain enough information to agree with fully retarded electrodynamics simulations, 2) those same simulations conform to the results from an updated tight-binding model that incorporates retardation effects and all-particle interactions and 3) the unexpected mode switching exhibited by these magnetic systems is due to the interplay of the three parts of the fully reatrded electric field. Most notably, without the inclusion of the far-field term and all inter-particle interactions, no mode-switching is observed. With a working model and a basic physical understanding of these three systems, we now perform a series of computations to look at its tunable properties. In the previous section, the scale of the systems was changed. However, this would be impossible to manipulate in a laboratory. We focus on properties with experimental analogues, namely, the dielectric constant of the embedding medium and the nearest-neighbor spacing between nanoparticles.

@@

In order to justify the next set of model calculations, we refer to research on flowing liquid crystal over MNP aggregates and, in real-time, adjusting the refractive index of the MNP environment, influencing the resonance frequencies of the system\cite{odom_lasing}. We apply this concept to our tight-binding model to determine if this has any implications on the properties of magnetic oligomers. What we find is that, as expected, increasing the real-valued dielectric constant of the background decreases the resonance frequency of the collective modes. Furthermore, the embedding medium influences the energy-ordering of the eigenvalues. Results of one of our explorations are summarized in Figure~\ref{dielectric}. As the dielectric constant of the medium increases, the eigenmodes collapse onto each other, and eventually converge with the single-particle frequency. Because the modes collapse so quickly and appear to overlap at all values of $\varepsilon_b$, Figure~\ref{dielectric}b displays the difference in energy between all of the eigenmodes of each system. The values of $\varepsilon_b$ where the differences cross zero signify mode-crossing. 
From these two observations we conclude that increasing the dielectric constant of the embedding medium weakens the overall inter-particle interactions. However, this occurs differently for each of the parts of the interaction. All of the field terms contain similar $k$-dependence through $\alpha_{\textrm{sp}}'$ and the trigonometric terms. Focusing on the different $k$-dependence in each of the coupling contants (~\ref{elec_hammy_2}) reveals the infuence of the dielectric constant on the electric field. $g_{ij}^\textrm{NF}$ contains no other $k$-dependence, so the near-field contribution is reduced by one factor of $\varepsilon_b$.  $g_{ij}^\textrm{IF}$ is linear in $k$, so it is reduced by a factor of $\sqrt{\varepsilon_b}$. Lastly,  $g_{ij}^\textrm{FF}$ is quadratic in $k$, so all $\varepsilon_b$-dependence is removed, besides that dependence previously mentioned. At higher values of the dielectric constant the far-field term dominates, much like the way particles that are far apart interact primarily through their far-fields (Figure~\ref{dimers}b and d). In other words, embedding magnetic systems in some dielectric medium causes them to act as though they are larger, effectively increasing their scale. This insight provides an experimental route to directly choosing the energy-ordering of magnetic modes, but the reduced splitting between modes might make such an experiment infeasible.

\begin{figure}
\centering
\includegraphics{spacing_study.pdf}
\caption{Magnetic mode eigenvalues for the twomer (first row), linear threemer (second row), and triangular threemer (third row) with particle sizes of 15 nm (column a) and 30 nm (column b) as a function of nearest neighbor particle separation in units of radii. As the separation distance increases, the magnetic mode eigenvalues converge to and oscillate about the single particle frequency, exhibiting multiple crossings. As in Equation~\ref{elec_hammy_2}, the interaction strength decays with increasing separation and oscillates due to its dependence on trigonometric functions.}
\label{spacing}
\end{figure}

Another topic of great interest is tuning the size and shape of a plasmonic aggregate using various polymers\cite{Ginger2017} or DNA\cite{DanLuo2009,NaLiu2017}. Here, we implement the idea of continuously distorting the nearest-neighbor spacing, from touching to tens of radii apart. We present data for particle radii of 15 nm and 30 nm in Figure~\ref{spacing}a and b, respectively. The results of these model calculations are reminiscent of the results in Figure~\ref{dimers} in that the eigenmodes oscillate about each other as the particles move farther apart. In addition, similarly to Figure~\ref{dielectric}, at very large distances the eigenvalues converge to the single LSPR frequency, exhibiting small amplitude oscillations. This is indicative of the coupling falling very near to zero. It is clear that this method, as opposed to the method of tuning the dielectric constant of the background, offers a much greater degree of tunability. Designing a system in which the inter-particle spacing could be varied in discrete steps would lead to the ability to directly choose the resonance frequency of a specific magnetic mode. Furthermore, being able to directly detect the frequency of the magnetic mode optically could turn such magnetic systems into thermometers, pH probes, or detectors of any environmental factor that would change the size of the embedding polymer.
